A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-11 paper/theor-experiment.tex
staring to edit last section

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are calculated at 
$s_3=19.4$~[m], see Fig.~\ref{awa-tba}.

\begin{align}
\text{min}  \quad & \text{rms}_{x}\left(s = s_3\right), \quad \text{rms}_{y}\left(s = s_3\right) \label{eq:awa:p1}\\
& \text{rms}_{px}\left(s = s_3\right), \quad \text{rms}_{py}\left(s = s_3\right), \label{eq:awa:p2}\\
& \text{rms}_{s}\left(s = s_3\right), \quad dE \label{eq:awa:p4} \\
\text{subject to} \quad & rms_x(s=s_1) < 0.1 \, [m]\label{eq:awa:c1}\\
\quad & rms_y(s=s_1) < 0.1\, [m]\label{eq:awa:c2}\\
\quad & |rms_y(s=s_1) - rms_x(s=s_1) | < 0.005 \, [m]\label{eq:awa:c3}\\
\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
at the location of interest in the beam line ($s_3$).
%Where $s_3$ is the longitudinal entrance of the fifth quadrupole. 
Minimizing the beam size at this location is essential to 
to preventing loss of particles by scraping.
Preventing scraping ensures better transmission through the wakefield structures downstream. 
Less divergence in the beam (lower transverse momentum) 
reduces growth of transverse beam size during transport in bending elements, 
which also helps with transmission downstream. 
The next two objectives (\ref{eq:awa:p2}) minimize the 
longitudinal beam size ($rms_s$), and energy spread (dE) at $s_1$.
This helps reduce longitudinal beam size growth in bending elements.

>>>>

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are weighted 
equally and calculated at 
$s_3=19.4$~[m], see Fig.~\ref{awa-tba}. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
at the location of interest in the beam line ($s_3$).
%Where $s_3$ is the longitudinal entrance of the fifth quadrupole. 
Minimizing the beam size at this location is essential to 
to preventing loss of particles by scraping; 
which ensures better transmission through the wakefield structures downstream. 
Less divergence in the beam (lower transverse momentum) 
reduces growth of transverse beam size after the focal point (min beam size).
This reduces halo by ensuring the beam is not over focused through a hard waist.
The momentum is also critical to preventing large growth during transport in bending elements. 
All of these factors help with transmission downstream.

The next two objectives in Eq. (\ref{eq:awa:p4}) minimize the 
longitudinal beam size ($rms_s$), and energy spread (dE) at $s_3$.
This helps reduce longitudinal beam size growth in bending elements.
A small bunch length ($rms_s$) is also critical.......
